\section{Acknowledgments}
In the spring of 2008 I had been working as an systems engineer for the S&IS division
of Boeing %%aircraft company
for a year and a half. I obtained an undergraduate degree in physics and mathematics 
from Rensselaer Polytechnic Institute in 2007, a university which was, concidentally also
my grandfather's alma mater. 
At that time there were aspects
of my job that I enjoyed and aspects that I hated. I enjoyed learning how to mitigate
the hostile environment a spacecraft experiences in orbit, I enjoyed working
with my then mentor Dr. Thomas Sutherland. I enjoyed the free time
and money that job gave me to pursue SCUBA diving semi-professionally. 

I made the decision
to terminate my employment and either become a SCUBA diving instructor or
get a Ph.D. in physics. Luckily, I was accepted to the physics PhD program at the University of Wisconsin
Madison. 

I grew up with two older sisters and three younger brothers, from an early age I had
an interest in taking things a part and putting them back together
whenever my brothers received a Lego kit for their birthday I
immediately took it and carefully assembled airplanes, cars, robots and had great
satisfaction doing this. Even though
I had a progressive upbringing a woman such as myself, who is interested in physics
mathematics and computer science, could not completely 
escape the prejudices of sexism. My friend's parents
told me that women are inherently worse at reading maps and telling 
directions and
even after I had obtained my master's in graduate school 
I was told that 'women just act, without thinking 
of the logic behind their actions'. Fortunately, these words and actions did not 
slow me down but propelled me forward. So while I watch many of my 
male colleagues pursue physics for purely personal interest part of my
purpose has always been to prove my worth. For this, I must thank my adversaries, 
without their outspoken disapproval at my decisions I might have 
settled for less. 

Thank you very much to my parents. My mother instilled a fire in me that will never 
go out and my father gave me the resilience to make sure the important things
always were accomplished. 
Thank you to my older sisters Laureen and Katherine who taught me how to stand up 
for myself but protected me when I needed it. Thank you to my little brothers, Daniel, Stephen
and Jimmy for giving me an opportunity to test out my managerial skills at an early age.

Thank you to the fantastic professors and staff at the University of Wisconsin Madison 
who encouraged me to overcome and thrive in a difficult environment.
Thank you to Professor Lisa Everett for teaching the hardest and most useful course I have ever had and
instilling in her students a drive for creative problem solving under pressure. 
Thank you to my graduate student colleagues who began with me in 2009, all 47 of you! 
My boyfriend, Aaron, if it weren't for you I probably would have keeled over due 
to malnourishment while I was taking courses and then you have put up with 
having a digital girlfriend for the last two years and
were always the first person to listen when anything went wrong.
Thank you to my colleague and mentor Michalis, arguing with you helped me hone my
skills for the meetings, and presentations you are a totally outstanding addition D%% abled D ??

As I sit on a boat in the Adaman sea off the coast of Thailand and watch the sun creep 
slowly above the horizon I've come to realize that challenges and adversity 
are only opportunities in disguise.
While my career as a SCUBA diving instructor has not developed further I am
satisfied with my decision. 