\section{Muon System}
Good muon detection and resolution is of central importance 
to the CMS detector due it's appearance in the final state of many important processes
(for example H$\rightarrow$ZZ$\rightarrow\mu\mu$ and H$\rightarrow\tau\tau$ 
with $\tau\rightarrow\mu\overbar{\nu_{\mu}}\nu_{\tau}$). 
The muon is a relatively easy particle to detect due to its long life time 
and heavy mass they are less affected by radiative losses and the
CMS detector is capable of reconstruction muon momentum and charge over the entire
kinematic range of the LHC. The muon system covers the region in pseudorapidity
$|\eta|<2.4$, consists of about 25,000 m$^{2}$ and is made up of 3
 different types of gaseous particle detectors: drift tube (DT) chambers, 
 cathode strip chambers (CSC) and resistive plate chambers (RPCs).
 Their selection and location are determined by the environmental
 changes with respect to pseudorapidity. %%%% check this
 
\subsection{Drift Tube System}
The barrel region has a low flux of neutrons (which are left over 
from hadronic decays), a uniform 3.8 T magnetic field and a low 
muon rate. Drift tube chambers with standard rectangular drift cells, 
which are more sensitive to  these environmental effects but are %%% Along with RPC'S?? CHECK THIS!!!
relatively cheaper and easier to produce, are used in this region. 
They cover the pseudorapidity $|\eta|<1.2$ and are stationed within 
the iron yoke. The barrel muon detector consists of 4 concentric
cylinders of drift tube chambers around the beam line. The 3 inner
cylinders have 60 DT chambers while the outer has 70 DT chambers,
these combine to a total of approximately 172,000 sensitive wires.

The DT Chambers are made up of three (or two) super-layers (SL), the 
SL is further divided into individual drift tube cells. 
A diagram of a drift cell is shown in figure ,%%%Drift cell figure
each drift cell contains an anode wire that is 50 $\mu$m in diameter
and two electrode plates that create the drift electric field. The walls
of the cell are grounded, acting as cathodes. Each cell is filled with a gas
mixture of 85\% Argon and 15\% Carbon Dioxide; the wire and the
electrodes are operated with a voltage difference of 1.8 kV. Each
SL is made of four layers of drift cells staggered by half a cell.
The wires of the inner SLs are aligned perpendicular to the beam line
to provide a measurement of the z position of the track while the 
outer SLs have wires aligned parallel to the beam line to 
to provide a measurement in the transverse plane. 

\subsection{Cathode Strip Chambers}
The Cathode Strip Chambers (CSC) are installed in the CMS barrel and the endcaps.
Due to their granularity and fast signal response time they are able to provide precision muon 
measurement and muon triggering in one device. 
CSCs do not require precise gas, temperature or pressure control and
are also capable of operating
in non-uniform magnetic fields which make them an ideal candidate for higher
ranges of pseudorapidity. 
As is illustrated in Figure %%%%add trapezoidal figure of CSCs
the CSCs consist of 7 trapezoidal panels with cathode strips which are interweaved with
6 planes of anode wires. Wires run azimuthally and define a track's 
radial component. The path of a charged muon is found by interpolating charges
on the cathode strips by the avalanche of positive ions which is catalyzed by
the charged muon. 
Muons from $1.2<|\eta|<2.4$ cross 3 or 4 CSCs. In total the CSC system provides
a combined 5000 m$^2$ of sensitive planes and have over 2 million wires.
The trapezoidal CSCs cover either 10$^{\o}$ or 20$^{\o}$ in $\phi$, all chambers
(excluding the ME1/3 ring) overlap to form continuous $\phi$ coverage.
Muons that traverse the region $0.9<|\eta|<1.2$ are also detected by resistive plate chambers. 
\subsection{Resistive Plate Chambers}
